Arrows for Parallel Computations

### 2017-12-17 paper/content/parrows.tex

Up until now we discussed Arrow operations more in detail, but in the following sections we focus on the dataflow instead of how the Arrows are obtained so we can focus on the important parts now that we have seen that Arrows are capable of expressing parallelism.

>>>>

Up until now we discussed Arrow operations more in detail, but in the following sections we focus more on the dataflow between the arrows, now that we have seen that Arrows are capable of expressing parallelism. We do however explain new concepts with more details if required for easier understanding.
